---
  title: "LFPSE Tables Comparison"
format: html
editor_options: 
  chunk_output_type: console
---
  
## Setup

```{r}

search_nrls <- FALSE
search_lfpse <- TRUE
search_steis <- FALSE

dataset <- "lfpse"

start_date <- "2024-01-01"
end_date <- "2024-03-31"

date_type <- "occurring" # "occurring" or "reported"

source("R/setup.R")

text_terms <- list(
  group_A = c("(?i)\\bparacetamol", "(?i)\\bco(-)?codamol"),
  group_B = c("(?i)\\bibuprofen"),
  group_C = c("(?i)\\bunwell")
)

text_filter <- expr((group_A | group_B) & group_C)

is_neopaed <- "none"

sampling_strategy <- "default"

include_term_tally_table <- "yes"

incident_level_required <- "yes"

list_of_tables_to_create_lfpse <- list(c(expr(max_physical_harm_level)))

summary_tables_incident_or_patient_level <- "patient"
```

## Old LFPSE Process

```{r}

tictoc::tic()

# filter for incidents where A001 contains the value 4
lfpse_categorical <- expr((' ' + A001 + ' ') %LIKE% '% 4 %')

# lfpse_categorical <- 0

if (lfpse_categorical == 0) {
  lfpse_categorical <- expr(1 == 1)
}

# get the latest revision and earliest submission date for each incident
latest_revision_table <-
  tbl(con_lfpse, in_schema("analysis", "Events")) |>
  group_by(Reference) |>
  summarise(
    Revision = max(Revision),
    reported_date = min(SubmissionDate)
  ) |>
  ungroup()

analysis_table_names <- c(
  "Metadata_Responses",
  "Incident_Responses",
  "Risk_Responses",
  "Outcome_Responses",
  "GoodCare_Responses",
  "EventDetails_Responses",
  "EventTime_Responses",
  "Location_Responses",
  "Events",
  "Patient_Responses",
  "Medication_Responses",
  "Devices_Responses",
  "Reporter_Responses",
  "Governance_Responses",
  # "Findings_Responses",
  "DmdMedication_Responses"
)

# load each table as a remote database reference
# rename EntityId to DmdEntityId in DmdMedication_Responses to avoid clash
analysis_tables <- lapply(analysis_table_names, function(x) {
  table <- tbl(con_lfpse, in_schema("analysis", x))
  if (x == "DmdMedication_Responses") {
    table <- table |> rename(DmdEntityId = EntityId)
  }
  return(table)
})

lfpse_analysis_tables <- c(list(latest_revision_table), analysis_tables)

# join tables on Reference and Revision, keeping rows in the latest revision table
lfpse_parsed <-
  purrr::reduce(
    lfpse_analysis_tables, left_join, by = c("Reference", "Revision")
  ) |>
  rename(occurred_date = T005) |>
  mutate(reported_date = sql('CAST("reported_date" AS DATE)')) |>
  mutate(P004_days = as.numeric(P004))

lfpse_filtered_categorical <- lfpse_parsed |>
  # apply date range filter and the categorical incident type filter
  filter(
    between(date_filter, start_date, end_date),
    lfpse_categorical
  ) |>
  # keep columns specified in the LFPSE rename lookup, plus patient age
  select(any_of(unname(rename_lookup[["LFPSE"]])), P004_days) |>
  # compute the most severe harm scores and patient count per incident
  group_by(Reference) |>
  mutate(
    OT001_min = min(as.numeric(OT001)),
    OT002_min = min(as.numeric(OT002)),
    npatient = max(EntityId)
  ) |>
  ungroup() |>
  # pull the query results from the database into local memory
  collect() |>
  mutate(
    # extract year and month from the chosen date column for aggregation
    year_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 1, 4)),
    month_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 6, 7)),
    # combine into a year-month value
    month_year_reported_or_occurred =
      zoo::as.yearmon(
        str_glue("{year_reported_or_occurred}-{month_reported_or_occurred}")
      ),
    # assign financial year
    financial_year_reported_or_occurred = ifelse(
      month_reported_or_occurred > 3,
      paste0(year_reported_or_occurred, '/', year_reported_or_occurred + 1),
      paste0(year_reported_or_occurred - 1, '/', year_reported_or_occurred)
    ),
    # convert month number to abbreviated name
    month_reported_or_occurred = month.abb[month_reported_or_occurred],
    reported_date = as.character(reported_date),
    occurred_date = as.character(occurred_date),
    # add 1 to psychological harm score so it sits on the same scale as physical harm
    OT002_min_plus_one = OT002_min + 1
  ) |>
  # compute the overall worst harm per row by taking the minimum across both
  # adjusted harm scores, min_safe handles cases where both are NA
  rowwise() |>
  mutate(max_harm = min_safe(c(OT001_min, OT002_min_plus_one))) |>
  ungroup() |>
  mutate(
    max_harm_level = case_when(
      max_harm == 1 ~ "Fatal",
      max_harm == 2 ~ "Severe harm",
      max_harm == 3 ~ "Moderate harm",
      max_harm == 4 ~ "Low harm",
      max_harm == 5 ~ "No harm"
    ),
    max_physical_harm_level = case_when(
      OT001_min == 1 ~ "Fatal",
      OT001_min == 2 ~ "Severe physical harm",
      OT001_min == 3 ~ "Moderate physical harm",
      OT001_min == 4 ~ "Low physical harm",
      OT001_min == 5 ~ "No physical harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    ),
    max_psychological_harm_level = case_when(
      OT002_min == 1 ~ "Severe psychological harm",
      OT002_min == 2 ~ "Moderate psychological harm",
      OT002_min == 3 ~ "Low psychological harm",
      OT002_min == 4 ~ "No psychological harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    )
  ) |>
  # drop intermediate columns
  select(-OT001_min, -OT002_min, -OT002_min_plus_one, -max_harm) |>
  # collapse multiple DMD rows per incident into a single row 
  group_by(across(-starts_with("DMD"))) |>
  summarise(
    across(
      starts_with("DMD"),
      ~ str_flatten(., collapse = ", "),
      .names = "{.col}"
    ),
    .groups = "drop"
  )

# text filters
lfpse_text_columns <- c(
  "F001", 
  "AC001", 
  "OT003", 
  "A008",
  "A008_Other", 
  "A002", 
  "DMD002", 
  "DMD004"
)

lfpse_filtered_text <- apply_text_search(
  lfpse_filtered_categorical,
  text_terms,
  text_filter,
  lfpse_text_columns,
  dataset
)

lfpse_labelled<- lfpse_filtered_text |>
  # pivot the coded columns
  pivot_longer(cols = any_of(ResponseReference$QuestionId)) |>
  # separate the multi-responses into single row per selection
  separate_rows(value, sep = " {~@~} ") |>
  # arrange so that multi-responses appear alphabetised later
  arrange(value) |>
  # bring through the value labels
  left_join(ResponseReference, by = c(
    "name" = "QuestionId",
    "value" = "ResponseCode",
    "TaxonomyVersion" = "TaxonomyVersion"
  )) |>
  # remove the unnecessary columns
  select(!c(value, Property, LastUpdated, IsActive)) |>
  # pivot back into columns
  pivot_wider(
    id_cols = !any_of(ResponseReference$QuestionId),
    names_from = name,
    values_from = ResponseText,
    # collapse multi-responses into single row per entity
    values_fn = list(ResponseText = ~ str_c(., collapse = "; "))
  ) 

# create a new column for age following validation 
lfpse_age_validated <- lfpse_labelled |>
  mutate(age_unit = case_when(
    is.na(P004_days) ~ 'age missing',
    between(P004_days, 1, 30) ~ 'days',
    between(P004_days, 31, 371) ~ 'months',
    between(P004_days, 372, 74028) ~ 'years',
    .default = 'age outside bounds')) |>
  mutate(age_compliance = case_when(
    age_unit == 'age outside bounds' ~ 'age outside bounds',
    age_unit == 'age missing' ~ 'age missing',
    age_unit == 'days' & between(P004_days, 1, 30) ~ 'yes',
    age_unit == 'months' & P004_days %% 31 == 0 ~ 'yes',
    age_unit == 'years' & P004_days %% 372 == 0 ~ 'yes',
    .default = 'no')) |>
  mutate(P004_days_validated = if_else(
    age_compliance == "yes", P004_days, NA
  ))

# age classification for neopaeds
lfpse_age_classified <- lfpse_age_validated |>
  mutate(
    concat_col = paste(
      F001, 
      AC001, 
      OT003, 
      # A008,
      A008_Other, 
      L006, 
      L006_Other, 
      sep = "_"
    ),
    age_category = case_when(
      (P004_days_validated > 0 & P004_days_validated <= 28) | 
        (P007 %in% c("0-14 days", "15-28 days")) ~ "neonate",
      (P004_days_validated > 28 & P004_days_validated < 6696) | 
        (P007 %in% c("1-11 months", "1-4 years", "5-9 years", "10-15 years", "16 and 17 years")) ~ "paediatric",
      (!is.na(P007) | !is.na(P004_days_validated)) ~ 'adult estimated',
      is.na(P004_days_validated) ~ 'unknown',# includes those where age is below zero / above believable threshold
      .default = 'other' 
    ),
    
    neonate_specialty_flag = str_detect(L006, neonatal_specialty_terms),
    neonate_terms_flag = str_detect(concat_col, neonatal_terms),
    missing_specialty = is.na(L006),
    no_adult_specialty_flag = str_detect(L006, adult_specialty_terms, negate = TRUE), 
    paediatric_specialty_flag = str_detect(L006, paediatric_specialty_terms),
    paediatric_term_flag = str_detect(concat_col, paediatric_terms),
    
    neonate_category = case_when(
      age_category == 'neonate' ~ "neonate_by_age",
      neonate_specialty_flag ~ "neonate_by_specialty",
      (neonate_terms_flag & (no_adult_specialty_flag | missing_specialty)) ~ "neonate_by_text",
      .default = "not neonate related"
    ),
    
    paediatric_category = case_when(
      age_category == 'paediatric' ~ "paediatric_by_age",
      paediatric_specialty_flag ~ "paediatric_by_specialty",
      (paediatric_term_flag & (no_adult_specialty_flag | missing_specialty)) ~ "paediatric_by_text",
      .default = "not paediatric related"
    )
  )

# Apply neopaed filter
lfpse_neopaed <- filter_by_neopaed_strategy(lfpse_age_classified, is_neopaed)


# Sampling
lfpse_sampled <- apply_sampling_strategy(
  lfpse_neopaed,
  sampling_strategy,
  harm_column = "OT001",
  death_severe_values = c("Fatal", "Severe physical harm"),
  moderate_values = c("Moderate physical harm"),
  reference_column = "Reference"
)

# Rename columns
lfpse_neopaed <- lfpse_neopaed |>
  select(any_of(rename_lookup[["LFPSE"]]), starts_with("group_")) 

lfpse_sampled <- lfpse_sampled |>
  select(any_of(rename_lookup[["LFPSE"]]), starts_with("group_")) 

# Create patient level tables
lfpse_for_release_sampled_pt_level <- lfpse_sampled |> 
  select(!c(contains("_term_"), `Month`, `Year`, `Month - Year`)) 

lfpse_for_release_unsampled_pt_level <- lfpse_neopaed |> 
  select(!c(contains("_term_"), `Month`, `Year`, `Month - Year`))

# Get data for summary tables
lfpse_for_summary_table_unsampled <- lfpse_neopaed  
lfpse_for_summary_table_sampled <- lfpse_sampled  

# Handle incident vs patient level for summary tables
if (summary_tables_incident_or_patient_level == "incident") {
  lfpse_for_summary_table_unsampled <- lfpse_for_summary_table_unsampled |>
    # remove columns that contain patient specific info (for summary tables)
    select(-any_of(c("Patient no.",
                     "OT001 - Physical harm",
                     "OT002 - Psychological harm",
                     "P004 - Age in days", 
                     "P007 - Age Range",
                     "OT003 - What was the clinical outcome for the patient?"
    ))) |> 
    distinct(Reference, .keep_all = TRUE)
  
  lfpse_for_summary_table_sampled <- lfpse_for_summary_table_sampled |>
    select(-any_of(c("Patient no.",
                     "OT001 - Physical harm",
                     "OT002 - Psychological harm",
                     "P004 - Age in days", 
                     "P007 - Age Range",
                     "OT003 - What was the clinical outcome for the patient?"
    ))) |> 
    distinct(Reference, .keep_all = TRUE)
}

# Log final counts
log_final_counts(
  dataset,
  lfpse_for_summary_table_unsampled,
  lfpse_for_summary_table_sampled,
  lfpse_for_release_unsampled_pt_level,
  lfpse_for_release_sampled_pt_level
)

tictoc::toc()
```

## New LFPSE Process

This is the new process which uses the new LFPSE table. The new `vwEventsTransposedAll` view is a flattened table that combines everything, meaning the processor no longer needs to do multiple joins.

The `vwTransposedAll` view joins the `EventsTransposed` and `EventsTransposedAdditionalPatients` tables, to include all patients.

However, the additional patient rows only include any information not recorded in the transposed events table, and other values are NA. This was causing some issues with the original process for queries, leading to a lot of additional patient rows being filtered out. Now the process below starts by identifying the references that meet the criteria for the query (`valid_refs`) and using this to filter for all incidents for the query (there may be a cleaner, more efficient approach to do this).

```{r}

tictoc::tic()

# filter for incidents where A001_InvolvedAgents contains the value 4
lfpse_categorical <- expr((' ' + A001_InvolvedAgents + ' ') %LIKE% '% 4 %')
# lfpse_categorical <- 0
if (lfpse_categorical == 0) {
  lfpse_categorical <- expr(1 == 1)
}

# load the all patients view
lfpse_analysis_table_new <-
  tbl(con_lfpse, in_schema("analysis", "vwEventsTransposedAll"))

# primary_table <-
#   tbl(con_lfpse, in_schema("analysis", "vwEventsTransposed"))

# Original column names for SQL
sql_date_filter <- if (date_type == 'occurring') expr(OccurredDate) else expr(OriginalSubmissionDate)

# Renamed column names for post-collect R code (unchanged from current)
date_filter <- if (date_type == 'occurring') expr(occurred_date) else expr(reported_date)

# identify the set of references that meet the date range and category criteria
# valid_refs <-
#   lfpse_analysis_table_new |>
#   filter(
#     EntityId == 1L, # removed NA to speed things up - keep an eye on potential issues
#     between(!!sql_date_filter, start_date, end_date),
#     lfpse_categorical
#   ) |>
#   select(Reference)

lfpse_filtered_categorical_new <-
  lfpse_analysis_table_new |>
  # inner_join(valid_refs, by = "Reference") |> 
  inner_join(
    lfpse_analysis_table_new |>
      filter(
        EntityId == 1L, # removed NA to speed things up - keep an eye on potential issues
        between(!!sql_date_filter, start_date, end_date),
        lfpse_categorical
      ) |>
      select(Reference),
    by = "Reference"
  ) |>
  select(any_of(unname(rename_lookup[["LFPSE_new"]])), P004_AgeAtTimeOfIncidentDays) |>
  # pull results from the database into local memory
  collect() |>
  # compute the most severe harm scores and patient count per incident
  mutate(
    occurred_date = OccurredDate, reported_date = OriginalSubmissionDate,
    P004_AgeAtTimeOfIncidentDays = as.numeric(P004_AgeAtTimeOfIncidentDays),
    OT001_min = min(as.numeric(OT001_PhysicalHarm), na.rm = FALSE),
    OT002_min = min(as.numeric(OT002_PsychologicalHarm), na.rm = FALSE),
    npatient = max(EntityId, na.rm = FALSE),
    .by = Reference
  ) |>
  mutate(
    # extract year and month
    year_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 1, 4)),
    month_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 6, 7)),
    # combine into year-month
    month_year_reported_or_occurred =
      zoo::as.yearmon(
        str_glue("{year_reported_or_occurred}-{month_reported_or_occurred}")
      ),
    # assign financial year
    financial_year_reported_or_occurred = ifelse(
      month_reported_or_occurred > 3,
      paste0(year_reported_or_occurred, '/', year_reported_or_occurred + 1),
      paste0(year_reported_or_occurred - 1, '/', year_reported_or_occurred)
    ),
    month_reported_or_occurred = month.abb[month_reported_or_occurred],
    reported_date = as.character(reported_date),
    occurred_date = as.character(occurred_date),
    # adjust psychological harm score to match the physical harm scale
    OT002_min_plus_one = OT002_min + 1,
    # take the element-wise minimum across both adjusted scores
    # pmin is used because it is quicker (and results are the same)
    max_harm = pmin(OT001_min, OT002_min_plus_one, na.rm = FALSE),
    max_harm_level = case_when(
      max_harm == 1 ~ "Fatal",
      max_harm == 2 ~ "Severe harm",
      max_harm == 3 ~ "Moderate harm",
      max_harm == 4 ~ "Low harm",
      max_harm == 5 ~ "No harm"
    ),
    max_physical_harm_level = case_when(
      OT001_min == 1 ~ "Fatal",
      OT001_min == 2 ~ "Severe physical harm",
      OT001_min == 3 ~ "Moderate physical harm",
      OT001_min == 4 ~ "Low physical harm",
      OT001_min == 5 ~ "No physical harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    ),
    max_psychological_harm_level = case_when(
      OT002_min == 1 ~ "Severe psychological harm",
      OT002_min == 2 ~ "Moderate psychological harm",
      OT002_min == 3 ~ "Low psychological harm",
      OT002_min == 4 ~ "No psychological harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    )
  ) |>
  # drop intermediate columns
  select(-OT001_min, -OT002_min, -OT002_min_plus_one, -max_harm) |>
  # replace database separator token with a readable comma separator
  mutate(across(starts_with("DMD"), ~ str_replace_all(.x, fixed(" {~@~} "), ", ")))


# text filters
lfpse_text_columns_new <- c(
  "F001_Description",
  "AC001_ImmediateActions",
  "OT003_ClinicalOutcome",
  "A008_DeviceType",
  "A008_Other_DeviceTypeOther",
  "A002_DrugsInvolved",
  "DMD002_VTMString",
  "DMD004_VMPString"
  )

lfpse_filtered_text_new <- apply_text_search(
  lfpse_filtered_categorical_new,
  text_terms,
  text_filter,
  lfpse_text_columns_new,
  dataset
)

question_cols_pattern <- paste0("^(", paste(unique(ResponseReference$QuestionId), collapse = "|"), ")(_|$)") 
  
lfpse_labelled_new <- lfpse_filtered_text_new |>
  mutate(across(matches(question_cols_pattern), as.character)) |>
  # match columns based on code (before underscore)
  pivot_longer(cols = matches(question_cols_pattern)) |>
  separate_rows(value, sep = " {~@~} ") |>
  # possibly remove the arrange because this is cosmetic and will (possibly) have significant performance costs?
  # arrange(value) |>
  # extract code
  mutate(QuestionId = str_extract(name, "^[^_]+")) |>
  left_join(ResponseReference, by = c(
    "QuestionId" = "QuestionId",
    "value" = "ResponseCode",
    "TaxonomyVersion" = "TaxonomyVersion"
    )) |>
  select(!c(value, QuestionId, Property, LastUpdated, IsActive)) |>
  pivot_wider(
    id_cols = !any_of(ResponseReference$QuestionId),
    names_from = name,
    values_from = ResponseText,
    values_fn  = list(ResponseText = ~ str_c(., collapse = "; "))
    )
  
# create a new column for age following validation 
lfpse_age_validated_new <- lfpse_labelled_new |>
  mutate(
    age_unit = case_when(
      is.na(P004_AgeAtTimeOfIncidentDays) ~ 'age missing',
      between(P004_AgeAtTimeOfIncidentDays, 1, 30) ~ 'days',
      between(P004_AgeAtTimeOfIncidentDays, 31, 371) ~ 'months',
      between(P004_AgeAtTimeOfIncidentDays, 372, 74028) ~ 'years',
      .default = 'age outside bounds'
      ),
    age_compliance = case_when(
      age_unit == 'age outside bounds' ~ 'age outside bounds',
      age_unit == 'age missing' ~ 'age missing',
      age_unit == 'days' & between(P004_AgeAtTimeOfIncidentDays, 1, 30) ~ 'yes',
      age_unit == 'months' & P004_AgeAtTimeOfIncidentDays %% 31 == 0 ~ 'yes',
      age_unit == 'years' & P004_AgeAtTimeOfIncidentDays %% 372 == 0 ~ 'yes',
      .default = 'no'
      ),
    P004_days_validated = if_else(age_compliance == "yes", P004_AgeAtTimeOfIncidentDays, NA)
    )
  
# age classification for neopaeds
lfpse_age_classified_new <- lfpse_age_validated_new |>
    mutate(
      concat_col = paste(
        F001_Description, 
        AC001_ImmediateActions, 
        OT003_ClinicalOutcome, 
        A008_DeviceType,
        A008_Other_DeviceTypeOther, 
        L006_ResponsibleSpecialty, 
        L006_Other_ResponsibleSpecialtyOther, 
        sep = "_"
        ),
      age_category = case_when(
        (P004_days_validated > 0 & P004_days_validated <= 28) | 
          (P007_AgeBracket %in% c("0-14 days", "15-28 days")) ~ "neonate",
        (P004_days_validated > 28 & P004_days_validated < 6696) | 
          (P007_AgeBracket %in% c("1-11 months", "1-4 years", "5-9 years", "10-15 years", "16 and 17 years")) ~ "paediatric",
        (!is.na(P007_AgeBracket) | !is.na(P004_days_validated)) ~ 'adult estimated',
        is.na(P004_days_validated) ~ 'unknown',# includes those where age is below zero / above believable threshold
        .default = 'other' 
      ),
      
      neonate_specialty_flag = str_detect(L006_ResponsibleSpecialty, neonatal_specialty_terms),
      neonate_terms_flag = str_detect(concat_col, neonatal_terms),
      missing_specialty = is.na(L006_ResponsibleSpecialty),
      no_adult_specialty_flag = str_detect(L006_ResponsibleSpecialty, adult_specialty_terms, negate = TRUE), 
      paediatric_specialty_flag = str_detect(L006_ResponsibleSpecialty, paediatric_specialty_terms),
      paediatric_term_flag = str_detect(concat_col, paediatric_terms),
      
      neonate_category = case_when(
        age_category == 'neonate' ~ "neonate_by_age",
        neonate_specialty_flag ~ "neonate_by_specialty",
        (neonate_terms_flag & (no_adult_specialty_flag | missing_specialty)) ~ "neonate_by_text",
        .default = "not neonate related"
      ),
      
      paediatric_category = case_when(
        age_category == 'paediatric' ~ "paediatric_by_age",
        paediatric_specialty_flag ~ "paediatric_by_specialty",
        (paediatric_term_flag & (no_adult_specialty_flag | missing_specialty)) ~ "paediatric_by_text",
        .default = "not paediatric related"
      )
    )
  
# Apply neopaed filter
lfpse_neopaed_new <- filter_by_neopaed_strategy(lfpse_age_classified_new, is_neopaed)

    
# Sampling
lfpse_sampled_new <- apply_sampling_strategy(
  lfpse_neopaed_new,
  sampling_strategy,
  harm_column = "OT001_PhysicalHarm",
  death_severe_values = c("Fatal", "Severe physical harm"),
  moderate_values = c("Moderate physical harm"),
  reference_column = "Reference"
  )
    
# Rename columns
lfpse_neopaed_new <- lfpse_neopaed_new |>
  select(any_of(rename_lookup[["LFPSE_new"]]), starts_with("group_")) 
    
lfpse_sampled_new <- lfpse_sampled_new |>
  select(any_of(rename_lookup[["LFPSE_new"]]), starts_with("group_")) 
    
# Create patient level tables
lfpse_for_release_sampled_pt_level_new <- lfpse_sampled_new |> 
  select(!c(contains("_term_"), `Month`, `Year`, `Month - Year`)) 
    
lfpse_for_release_unsampled_pt_level_new <- lfpse_neopaed_new |> 
  select(!c(contains("_term_"), `Month`, `Year`, `Month - Year`))
    
# Get data for summary tables
lfpse_for_summary_table_unsampled_new <- lfpse_neopaed_new  
lfpse_for_summary_table_sampled_new <- lfpse_sampled_new  
    
# Handle incident vs patient level for summary tables
if (summary_tables_incident_or_patient_level == "incident") {
  lfpse_for_summary_table_unsampled_new <- lfpse_for_summary_table_unsampled_new |>
    # remove columns that contain patient specific info (for summary tables)
    select(-any_of(c("Patient no.",
                     "OT001 - Physical harm",
                     "OT002 - Psychological harm",
                     "P004 - Age in days", 
                     "P007 - Age Range",
                     "OT003 - What was the clinical outcome for the patient?"
                     ))) |> 
  distinct(Reference, .keep_all = TRUE)
  
  lfpse_for_summary_table_sampled_new <- lfpse_for_summary_table_sampled_new |>
    select(-any_of(c("Patient no.",
                     "OT001 - Physical harm",
                     "OT002 - Psychological harm",
                     "P004 - Age in days", 
                     "P007 - Age Range",
                     "OT003 - What was the clinical outcome for the patient?"
                     ))) |> 
    distinct(Reference, .keep_all = TRUE)
    }
    
# Log final counts
log_final_counts(
  dataset,
  lfpse_for_summary_table_unsampled_new,
  lfpse_for_summary_table_sampled_new,
  lfpse_for_release_unsampled_pt_level_new,
  lfpse_for_release_sampled_pt_level_new
)


tictoc::toc()
```

## Comparison

### Row Counts

```{r}

# compare total row counts between old and new pipelines
nrow(lfpse_filtered_categorical_new) - nrow(lfpse_filtered_categorical)
nrow(lfpse_filtered_text_new) - nrow(lfpse_filtered_text)
nrow(lfpse_labelled_new) - nrow(lfpse_labelled)
nrow(lfpse_sampled_new) - nrow(lfpse_sampled)

# compare distinct incident counts — negative value means old has more references
nrow(distinct(lfpse_filtered_categorical_new, Reference, EntityId)) -
  nrow(distinct(lfpse_filtered_categorical, Reference, EntityId))
```

### Reference

```{r}

# incidents in the old table but not in the new table
lfpse_filtered_text |>
  filter(!Reference %in% lfpse_filtered_text_new$Reference)

# incidents in the new table but not in the old table
lfpse_filtered_text_new |>
  filter(!Reference %in% lfpse_filtered_text$Reference)
```

### Differences

```{r}

full_join(
  lfpse_filtered_text |> count(Reference, name = "count_old"),
  lfpse_filtered_text_new |> count(Reference, name = "count_new"),
  by = "Reference"
) |>
  mutate(diff = count_new - count_old) |>
  filter(diff != 0)
```


