---
title: "LFPSE Tables Comparison"
format: html
editor_options: 
  chunk_output_type: console
---

## Setup

There are several packages, helper functions, and parameters that need to be set to run the LFPSE processor. 

```{r}

library(tidyr)
library(dplyr)
library(dbplyr)
library(stringr)
library(Microsoft365R)
library(zoo)
```

```{r}

# returns NA if all values are missing, otherwise returns the minimum non-NA value
min_safe <- function(vec) {
  ifelse(length(vec[!is.na(vec)]) == 0, NA_real_, min(vec, na.rm = TRUE))
}

# flags controlling which incident reporting systems to query
search_nrls <- F
search_lfpse <- T
search_steis <- F

# date range and whether to filter by date of occurrence or date of report
start_date <- "2024-01-01"
end_date <- "2024-12-31"
date_type <- "occurring"

# load database connection settings and column name mappings
source("R/config/connections.R")
source("R/config/column_selection_lookups.R")

# set the date column to filter on, based on date_type above
date_filter <- if (date_type == 'occurring') {
  expr(occurred_date)
} else if (date_type == 'reported') {
  expr(reported_date)
}
```

## Old LFPSE Process

This is the same process currently being used in the data request pipeline.

```{r}

# filter for incidents where A001 contains the value 4
lfpse_categorical <- expr((' ' + A001 + ' ') %LIKE% '% 4 %')

# get the latest revision and earliest submission date for each incident
latest_revision_table <-
  tbl(con_lfpse, in_schema("analysis", "Events")) |>
  group_by(Reference) |>
  summarise(
    Revision = max(Revision),
    reported_date = min(SubmissionDate)
  ) |>
  ungroup()

analysis_table_names <- c(
  "Metadata_Responses",
  "Incident_Responses",
  "Risk_Responses",
  "Outcome_Responses",
  "GoodCare_Responses",
  "EventDetails_Responses",
  "EventTime_Responses",
  "Location_Responses",
  "Events",
  "Patient_Responses",
  "Medication_Responses",
  "Devices_Responses",
  "Reporter_Responses",
  "Governance_Responses",
  # "Findings_Responses",
  "DmdMedication_Responses"
)

# load each table as a remote database reference
# rename EntityId to DmdEntityId in DmdMedication_Responses to avoid clash
analysis_tables <- lapply(analysis_table_names, function(x) {
  table <- tbl(con_lfpse, in_schema("analysis", x))
  if (x == "DmdMedication_Responses") {
    table <- table |> rename(DmdEntityId = EntityId)
  }
  return(table)
})

lfpse_analysis_tables <- c(list(latest_revision_table), analysis_tables)

# join tables on Reference and Revision, keeping rows in the latest revision table
lfpse_parsed <-
  purrr::reduce(
    lfpse_analysis_tables, left_join, by = c("Reference", "Revision")
  ) |>
  rename(occurred_date = T005) |>
  mutate(reported_date = sql('CAST("reported_date" AS DATE)')) |>
  mutate(P004_days = as.numeric(P004))

lfpse_filtered_categorical <- lfpse_parsed |>
  # apply date range filter and the categorical incident type filter
  filter(
    between(date_filter, start_date, end_date),
    lfpse_categorical
  ) |>
  # keep columns specified in the LFPSE rename lookup, plus patient age
  select(any_of(unname(rename_lookup[["LFPSE"]])), P004_days) |>
  # compute the most severe harm scores and patient count per incident
  group_by(Reference) |>
  mutate(
    OT001_min = min(as.numeric(OT001)),
    OT002_min = min(as.numeric(OT002)),
    npatient = max(EntityId)
  ) |>
  ungroup() |>
  # pull the query results from the database into local memory
  collect() |>
  mutate(
    # extract year and month from the chosen date column for aggregation
    year_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 1, 4)),
    month_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 6, 7)),
    # combine into a year-month value
    month_year_reported_or_occurred =
      zoo::as.yearmon(
        str_glue("{year_reported_or_occurred}-{month_reported_or_occurred}")
      ),
    # assign financial year
    financial_year_reported_or_occurred = ifelse(
      month_reported_or_occurred > 3,
      paste0(year_reported_or_occurred, '/', year_reported_or_occurred + 1),
      paste0(year_reported_or_occurred - 1, '/', year_reported_or_occurred)
    ),
    # convert month number to abbreviated name
    month_reported_or_occurred = month.abb[month_reported_or_occurred],
    reported_date = as.character(reported_date),
    occurred_date = as.character(occurred_date),
    # add 1 to psychological harm score so it sits on the same scale as physical harm
    OT002_min_plus_one = OT002_min + 1
  ) |>
  # compute the overall worst harm per row by taking the minimum across both
  # adjusted harm scores, min_safe handles cases where both are NA
  rowwise() |>
  mutate(max_harm = min_safe(c(OT001_min, OT002_min_plus_one))) |>
  ungroup() |>
  mutate(
    max_harm_level = case_when(
      max_harm == 1 ~ "Fatal",
      max_harm == 2 ~ "Severe harm",
      max_harm == 3 ~ "Moderate harm",
      max_harm == 4 ~ "Low harm",
      max_harm == 5 ~ "No harm"
    ),
    max_physical_harm_level = case_when(
      OT001_min == 1 ~ "Fatal",
      OT001_min == 2 ~ "Severe physical harm",
      OT001_min == 3 ~ "Moderate physical harm",
      OT001_min == 4 ~ "Low physical harm",
      OT001_min == 5 ~ "No physical harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    ),
    max_psychological_harm_level = case_when(
      OT002_min == 1 ~ "Severe psychological harm",
      OT002_min == 2 ~ "Moderate psychological harm",
      OT002_min == 3 ~ "Low psychological harm",
      OT002_min == 4 ~ "No psychological harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    )
  ) |>
  # drop intermediate columns
  select(-OT001_min, -OT002_min, -OT002_min_plus_one, -max_harm) |>
  # collapse multiple DMD rows per incident into a single row 
  group_by(across(-starts_with("DMD"))) |>
  summarise(
    across(
      starts_with("DMD"),
      ~ str_flatten(., collapse = ", "),
      .names = "{.col}"
    ),
    .groups = "drop"
  )
```

## New LFPSE Process

This is the new process which uses the new LFPSE table. The new `vwEventsTransposedAll` view is a flattened table that combines everything, meaning the processor no longer needs to do multiple joins.

The `vwTransposedAll` view joins the `EventsTransposed` and `EventsTransposedAdditionalPatients` tables, to include all patients.

However, the additional patient rows only include any information not recorded in the transposed events table, and other values are NA. This was causing some issues with the original process for queries, leading to a lot of additional patient rows being filtered out. Now the process below starts by identifying the references that meet the criteria for the query (`valid_refs`) and using this to filter for all incidents for the query (there may be a cleaner, more efficient approach to do this).

```{r}

# filter for incidents where A001_InvolvedAgents contains the value 4
lfpse_categorical <- expr((' ' + A001_InvolvedAgents + ' ') %LIKE% '% 4 %')

# load the all patients view
lfpse_analysis_table_new <-
  tbl(con_lfpse, in_schema("analysis", "vwEventsTransposedAll"))

# identify the set of references that meet the date range and category criteria
valid_refs <-
  lfpse_analysis_table_new |>
  mutate(occurred_date = OccurredDate) |>
  filter(
    EntityId == 1 | is.na(EntityId),
    between(date_filter, start_date, end_date),
    lfpse_categorical
  ) |>
  select(Reference) |>
  distinct()

lfpse_filtered_categorical_new <-
  lfpse_analysis_table_new |>
  # restrict to only the valid references identified above
  inner_join(valid_refs, by = "Reference") |>
  mutate(
    occurred_date = OccurredDate,
    reported_date = OriginalSubmissionDate,
    P004_AgeAtTimeOfIncidentDays = as.numeric(P004_AgeAtTimeOfIncidentDays)
  ) |>
  # compute the most severe harm scores and patient count per incident
  mutate(
    OT001_min = min(as.numeric(OT001_PhysicalHarm), na.rm = FALSE),
    OT002_min = min(as.numeric(OT002_PsychologicalHarm), na.rm = FALSE),
    npatient = max(EntityId, na.rm = FALSE),
    .by = Reference
  ) |>
  # pull results from the database into local memory
  collect() |>
  mutate(
    # extract year and month
    year_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 1, 4)),
    month_reported_or_occurred =
      as.numeric(substr(as.character(!!date_filter), 6, 7)),
    # combine into year-month
    month_year_reported_or_occurred =
      zoo::as.yearmon(
        str_glue("{year_reported_or_occurred}-{month_reported_or_occurred}")
      ),
    # assign financial year
    financial_year_reported_or_occurred = ifelse(
      month_reported_or_occurred > 3,
      paste0(year_reported_or_occurred, '/', year_reported_or_occurred + 1),
      paste0(year_reported_or_occurred - 1, '/', year_reported_or_occurred)
    ),
    month_reported_or_occurred = month.abb[month_reported_or_occurred],
    reported_date = as.character(reported_date),
    occurred_date = as.character(occurred_date),
    # adjust psychological harm score to match the physical harm scale
    OT002_min_plus_one = OT002_min + 1,
    # take the element-wise minimum across both adjusted scores
    # pmin is used because it is quicker (and results are the same)
    max_harm = pmin(OT001_min, OT002_min_plus_one, na.rm = FALSE),
    max_harm_level = case_when(
      max_harm == 1 ~ "Fatal",
      max_harm == 2 ~ "Severe harm",
      max_harm == 3 ~ "Moderate harm",
      max_harm == 4 ~ "Low harm",
      max_harm == 5 ~ "No harm"
    ),
    max_physical_harm_level = case_when(
      OT001_min == 1 ~ "Fatal",
      OT001_min == 2 ~ "Severe physical harm",
      OT001_min == 3 ~ "Moderate physical harm",
      OT001_min == 4 ~ "Low physical harm",
      OT001_min == 5 ~ "No physical harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    ),
    max_psychological_harm_level = case_when(
      OT002_min == 1 ~ "Severe psychological harm",
      OT002_min == 2 ~ "Moderate psychological harm",
      OT002_min == 3 ~ "Low psychological harm",
      OT002_min == 4 ~ "No psychological harm",
      is.na(npatient) ~ "Not applicable",
      .default = "Harm level missing"
    )
  ) |>
  # drop intermediate columns
  select(-OT001_min, -OT002_min, -OT002_min_plus_one, -max_harm) |>
  # replace database separator token with a readable comma separator
  mutate(across(starts_with("DMD"), ~ str_replace_all(.x, fixed(" {~@~} "), ", ")))
```

## Comparison

### Row Counts

```{r}

# compare total row counts between old and new pipelines
nrow(lfpse_filtered_categorical) - nrow(lfpse_filtered_categorical_new)

# compare distinct incident counts — positive value means old has more references
nrow(distinct(lfpse_filtered_categorical, Reference)) -
  nrow(distinct(lfpse_filtered_categorical_new, Reference))
```

There are currently 12 more rows in the old LFPSE table. Comparing distinct incidents shows the same, suggesting there are 12 distinct incidents that are not in the new LFPSE table.

### Reference

```{r}

# incidents in the old table but not in the new table
lfpse_filtered_categorical |>
  filter(!Reference %in% lfpse_filtered_categorical_new$Reference)

# incidents in the new table but not in the old table
lfpse_filtered_categorical_new |>
  filter(!Reference %in% lfpse_filtered_categorical$Reference)
```

There are 14 incidents that are in the old LFPSE table that don't show up in the new table, and two in the new table that are not in the old table.

I have checked this isn't caused by the way the valid incident references are being identified by running the base query (categorical and date filters) on `vwEventsTransposed`, producing the same discrepancy.

### Entity ID

```{r}

# count distinct entity id in each pipeline
nrow(distinct(lfpse_filtered_categorical_new, EntityId))
nrow(distinct(lfpse_filtered_categorical, EntityId))

# check for any rows in the old pipeline where EntityId is NA
lfpse_filtered_categorical |>
  filter(is.na(EntityId))

# filter both pipelines to single-patient records (EntityId == 1) for comparison
old_single_patient <- lfpse_filtered_categorical |>
  filter(EntityId == 1)

new_single_patient <- lfpse_filtered_categorical_new |>
  filter(EntityId == 1)

# compare row counts for single-patient records between pipelines
nrow(old_single_patient) - nrow(new_single_patient)

# filter incidents that don't appear in the new table where EntityId is NA 
lfpse_filtered_categorical |>
  filter(is.na(EntityId) & !Reference %in% lfpse_filtered_categorical_new$Reference)
```

There is a small difference in the distinct `EntityId` values in both tables. This is because there are rows in the old table where `EntityId` is NA. There are almost 25,000 rows where `EntityId` = NA in the old table. However, when filtering by `Reference` as well, it appears that most of the NAs correspond to incidents that are in the new table, but the `EntityId` is not missing.

When filtering out the extra patients, there is a big gap, which also seems to be caused primarily by the NAs (the difference is very similar to the number of EntityId = NA in the old table).

This might not be an issue, but I wanted to highlight it and double-check it is expected.

### DMD

There were previously some issues with DMD records in the new tables not including all medications, however those have now been fixed.

```{r}

# extract medication fields from each pipeline, excluding rows where both are NA,
# renaming new pipeline columns to match old pipeline names for comparison
old_dmd <- lfpse_filtered_categorical |>
  select(Reference, EntityId, Revision, DMD002, DMD004) |>
  filter(!is.na(DMD002) | !is.na(DMD004)) |>
  arrange(Reference)

new_dmd <- lfpse_filtered_categorical_new |>
  select(
    Reference, EntityId, Revision,
    DMD002 = DMD002_VTMString,
    DMD004 = DMD004_VMPString
  ) |>
  filter(!is.na(DMD002) | !is.na(DMD004)) |>
  arrange(Reference)

# show row-level differences in medication data between pipelines
diffdf::diffdf(old_dmd, new_dmd)

# medication records in the new pipeline with no match in the old
new_dmd |>
  filter(!Reference %in% old_dmd$Reference)
```

There are two incidents that don't appear in the new table, but this seems to be a separate issue to DMD. There are minor differences between the two tables, like the ordering of medications, but otherwise they appear to be the same.
