---
format: html
editor: visual
eval: false
echo: false
---

# Configuration

Configure all parameters for the data request. Modify the values below to set the requirements for the request.

## Database Selection

```{r}

search_nrls <- TRUE
search_lfpse <- TRUE
search_steis <- TRUE
```

## Date Range

Specify the date range and whether the dates are occurring or reported.

```{r}

start_date <- "2023-01-01"
end_date <- "2024-12-31"
date_type <- "occurring" # "occurring" or "reported"
```

# Setup

Load all required functions and establish database connections.

```{r}

source("R/setup.R")
```

## Column Extraction

```{r}

# cols to extract (all/default)
cols_to_extract <- "default"
```

## Categorical Filters

Define categorical filters for each database.

-   Wrap filter expressions in `expr()`.
-   Set to `0` for no filter.

`translate_categorical_string()` translates filters from the codes used to access the database to more human-readable code. It splits up filters by `&` (AND) or `|` (OR) and translates each filter one by one.

Examples:

``` r
nrls_categorical <- 
  expr((IN05_LVL1 == 10 | IN05_LVL2 == 3) & 
         (IN04 == 1 | IN04 %in% c(97, 99) & 
            !is.na(RP07) | is.na(IN04) & !is.na(RP07))) 
```

``` r
lfpse_categorical <- 
  expr((' ' + A001 + ' ') %LIKE% '% 4 %'| 
         ((' ' + A001 + ' ') %LIKE% '% 3 %' & 
            (' ' + A001 + ' ') %LIKE% '% 10 %'))
```

### NRLS

```{r}

nrls_categorical <- expr(IN05_LVL1 == 10)
```

### LFPSE

```{r}

lfpse_categorical <- expr((" " + A001 + " ") %LIKE% "% 4 %")
```

### StEIS

```{r}

steis_categorical <- expr(type_of_incident == "Medication incident meeting SI criteria")
steis_filename <- "SUI_2_87360.csv"
```

## Text Search

```{r}

# define search term groups
text_terms <- list(
  group_A = c("(?i)\\bparacetamol", "(?i)\\bco(-)?codamol"),
  group_B = c("(?i)\\bibuprofen"),
  group_C = c("(?i)\\bunwell")
)

# define how groups combine (using boolean logic)
text_filter <- expr((group_A | group_B) & group_C)

# to skip text search, use:
# text_terms <- list()
# text_filter <- expr(1 == 1)
```

## NeoPaed Classification

```{r}

# neopaed logic (neonate/paed/either/none)
is_neopaed <- "none"
```

## Sampling Strategy

```{r}

# sampling strategy (default/FOI/none)
sampling_strategy <- "default"
```

## Output Options

```{r}

include_term_tally_table <- "yes"

incident_level_required <- "yes"

write_to_sp <- TRUE
```

## Summary Tables

Examples:

``` r
list_of_tables_to_create_lfpse <- list(
  c(expr(max_physical_harm_level)),
  c(expr(year_reported_or_occurred), expr(month_reported_or_occurred)),
  c(expr(month_year_reported_or_occurred), expr(max_physical_harm_level))
)
```

``` r
list_of_tables_to_create_steis <- list(
  c(expr(type_of_incident)),
  c(expr(year_reported_or_occurred))
)
```

``` r
list_of_tables_to_create_nrls <- list(
  c(expr(PD09)),
  c(expr(month_year_reported_or_occurred), expr(PD09))
)
```

```{r}

list_of_tables_to_create_lfpse <- list(c(expr(max_physical_harm_level)))
list_of_tables_to_create_steis <- list(c(expr(year_reported_or_occurred)))
list_of_tables_to_create_nrls <- list(c(expr(PD09)))

# should LFPSE summary tables be incident level or patient level? (incident/patient)
# note - if LFPSE is not searched, this will not have any effect
summary_tables_incident_or_patient_level <- "incident"
```

# Execute Request

```{r}

results <- run_data_request(
  # database selection
  search_nrls = search_nrls,
  search_lfpse = search_lfpse,
  search_steis = search_steis,
  
  # date parameters
  start_date = start_date,
  end_date = end_date,
  date_type = date_type,
  
  # categorical filters
  nrls_categorical = nrls_categorical,
  lfpse_categorical = lfpse_categorical,
  steis_categorical = steis_categorical,
  steis_filename = steis_filename,
  
  # text filters
  text_terms = text_terms,
  text_filter = text_filter,
  
  # classification
  is_neopaed = is_neopaed,
  
  
  # sampling
  sampling_strategy = sampling_strategy,
  
  # output configuration
  include_term_tally_table = include_term_tally_table,
  incident_level_required = incident_level_required,
  write_to_sp = write_to_sp,
  
  # table specifications
  list_of_tables_to_create_lfpse = list_of_tables_to_create_lfpse,
  list_of_tables_to_create_steis = list_of_tables_to_create_steis,
  list_of_tables_to_create_nrls = list_of_tables_to_create_nrls,
  summary_tables_incident_or_patient_level = summary_tables_incident_or_patient_level
)
```
