---
format: html
editor: visual
eval: false
---

# Parameters which control flow

Write output to SharePoint.

```{r}
#this should be set to false during development of the template, but true when working on requests
write_to_sp <- TRUE
```

Specify datasets to be searched.

```{r}

search_nrls <- TRUE
search_lfpse <- TRUE
search_steis <- TRUE
```

# Setup

```{r}
#| label: renv-check

if (!requireNamespace("renv", quietly = TRUE)) {
  stop("renv not installed. Install with: install.packages('renv')")
}

if (!dir.exists("renv/library") || length(list.files("renv/library")) == 0){
  stop("renv library empty. Run renv::init() first.")
}
```

```{r}
#| label: imports

library(tidyverse)
library(dbplyr)
library(janitor)
library(here)
library(openxlsx)
library(glue)
library(Microsoft365R)
library(zoo)
```

Connect to relevant databases and import corresponding lookups for each connected database.

```{r}

# connect to (relevant) data bases and bring corresponding look ups
source("connections.R")
```

```{r}

source("functions.R") 
source("column_selection_lookups.R") # contains column names to be extracted
source("styles.R") #contains styles used by openxlsx
source("neopaeds.R") #contains search terms used to categorise incidents as neonate/paediatric
```

# Parameters

## Filter Parameters

Filter by date range and type

```{r}

start_date <- "2023-01-01"
end_date <- "2024-12-31"

# occurring or reported
date_type <- "occurring"
```

Categorical filters

```{r}

# nrls categorical filters (wrap in expr() or set to 0)
nrls_categorical <- expr(IN05_LVL1 == 10 )
# lfpse categorical filters (wrap in expr() or set to 0)
lfpse_categorical <- expr((' ' + A001 + ' ') %LIKE% '% 4 %')
# steis categorical filters (wrap in expr() or set to 0)
steis_categorical <- expr(type_of_incident == 'Medication incident meeting SI criteria')
steis_filename <- 'SUI_2_87360.csv'
```

Text filters

```{r}

# text terms
#example below- not real example
text_terms <- list(
  group_A = c("(?i)\\bparacetamol", "(?i)\\bco(-)?codamol"),
  group_B = c("(?i)\\bibuprofen"),
  group_C = c("(?i)\\bunwell")
)

text_filter <- expr((group_A | group_B) & group_C)

#text_terms<- list()
#text_filter<- expr(1 == 1)
```

Neopaed filter

```{r}

# neopaed logic (neonate/paed/either/none)
is_neopaed <- "none"
```

## Output Parameters

Is term tally table required?

```{r}

# do you want to include term/group tally tables in the summary sheets? "yes" or "no"
include_term_tally_table <- "yes"
```

Is incident level data required?

```{r}

# is incident level data required? "yes" or "no"
incident_level_required<- "yes"
```

What summary tables are required?

Create a list with an element containing a vector for each table you would like. The first element of the vector is what you want as rows, the second is what you want as columns (or you can just have one element). The month, year and month-year columns will be the date type specified in `date_type` Examples:

```         
list_of_tables_to_create_lfpse <- list(
  c(expr(max_physical_harm_level)),
  c(expr(year_reported_or_occurred),expr(month_reported_or_occurred)),
  c(expr(month_year_reported_or_occurred), expr(max_physical_harm_level))
  )
```

```         
list_of_tables_to_create_steis <- list(
  c(expr(type_of_incident)),
  c(expr(year_reported_or_occurred),expr(month_reported_or_occurred)),
  c(expr(month_year_reported_or_occurred),expr(type_of_incident))
  )
```

```         
list_of_tables_to_create_nrls <- list(
  c(expr(PD09)), 
  c(expr(year_reported_or_occurred),expr(month_reported_or_occurred)),
  c(expr(month_year_reported_or_occurred), expr(PD09))
  )
```

```{r}

list_of_tables_to_create_lfpse <- list(c(expr(max_physical_harm_level)))
list_of_tables_to_create_steis <- list(c(expr(year_reported_or_occurred)))
list_of_tables_to_create_nrls <- list(c(expr(PD09)))
```

Should LFPSE summary tables be incident level or patient level? (incident/patient)

```{r}

# ### Is term tally table required
#note- if LFPSE is not searched, this will not have any effect
summary_tables_incident_or_patient_level <- "patient"
```

Sampling Strategy

```{r}

# sampling strategy (default/FOI/none)
# TODO: custom
sampling_strategy <- "default"
```

What columns should be included (note, this only effects StEIS currently)

```{r}
# TODO: cols to extract (all/default)
cols_to_extract <- "default"

```

# Run Pipeline

```{r}

source("expand_categorical_filters.R")
```

```{r}

#start flow
source("flow.R")
```
