---
format: html
editor: visual
eval: false
---

# Parameters

## Setup

```{r}
#| label: renv-check

if (!requireNamespace("renv", quietly = TRUE)) {
  stop("renv not installed. Install with: install.packages('renv')")
}

if (!dir.exists("renv/library") || length(list.files("renv/library")) == 0){
  stop("renv library empty. Run renv::init() first.")
}
```

```{r}
#| label: imports

library(tidyverse)
library(dbplyr)
library(janitor)
library(here)
library(openxlsx)
library(glue)
library(Microsoft365R)
library(zoo)
```

Write output to SharePoint.

```{r}

write_to_sp <- TRUE
```

Specify datasets to be searched.

```{r}

search_nrls <- FALSE
search_lfpse <- TRUE
search_steis <- FALSE
```

Filter by date range and type.

```{r}

start_date <- "2023-01-01"
end_date <- "2024-12-31"

# occurring or reported
date_type <- "occurring"
```

## Source Connection & Helper Files

Connect to relevant databases and import corresponding lookups for each connected database.

```{r}

# connect to (relevant) data bases and bring corresponding look ups
source("connections.R")
```

```{r}

source("functions.R") 
source("column_selection_lookups.R") # contains column names to be extracted
source("styles.R") #contains styles used by openxlsx
source("neopaeds.R") #contains search terms used to categorise incidents as neonate/paediatric
```

## Filter Parameters

```{r}

# TODO: cols to extract (all/default)
cols_to_extract <- "default"
```

`translate_categorical_string()` can translate filters from the codes used to access the database, to more readable code.

It splits up filters by `&` or `|` and translates each filter one by one.

Some examples of filters it can translate are:

```         
nrls_categorical <- expr(
  (IN05_LVL1 == 10 | IN05_LVL2 == 3) & 
    (IN04 == 1 | IN04 %in% c(97, 99) & 
       !is.na(RP07) | is.na(IN04) & !is.na(RP07))
  )
```

```         
lfpse_categorical <- expr(
  (' ' + A001 + ' ') %LIKE% '% 4 %'| 
    ((' ' + A001 + ' ') %LIKE% '% 3 %' 
     & (' ' + A001 + ' ') %LIKE% '% 10 %')
  )
```

```{r}

# nrls categorical filters (wrap in expr() or set to 0)
nrls_categorical <- expr(IN05_LVL1 == 10 )
# lfpse categorical filters (wrap in expr() or set to 0)
lfpse_categorical <- expr((' ' + A001 + ' ') %LIKE% '% 4 %')
# steis categorical filters (wrap in expr() or set to 0)
steis_categorical <- expr(type_of_incident == 'Medication incident meeting SI criteria')
steis_filename <- 'SUI_2_87360.csv'
```

```{r}

# text terms
#example below- not real example
text_terms <- list(
  group_A = c("(?i)\\bparacetamol", "(?i)\\bco(-)?codamol"),
  group_B = c("(?i)\\bibuprofen"),
  group_C = c("(?i)\\bunwell")
)

text_filter <- expr((group_A | group_B) & group_C)

#text_terms<- list()
#text_filter<- expr(1 == 1)
```

```{r}

# neopaed logic (neonate/paed/either/none)
is_neopaed <- "none"
```

## Output Parameters

```{r}

# do you want to include term/group tally tables in the summary sheets? "yes" or "no"
include_term_tally_table <- "yes"
```

```{r}

# is incident level data required? "yes" or "no"
incident_level_required<- "yes"
```

Create a list with an element containing for each table you would like First element is what you want as rows, second is what you want as columns or you can just have one element The month, year and month-year columns will be the date type specified in `date_type` Examples:

```         
list_of_tables_to_create_lfpse <- list(
  c(expr(max_physical_harm_level)),
  c(expr(year_reported_or_occurred),expr(month_reported_or_occurred)),
  c(expr(month_year_reported_or_occurred), expr(max_physical_harm_level))
  )
```

```         
list_of_tables_to_create_steis <- list(
  c(expr(type_of_incident)),
  c(expr(year_reported_or_occurred),expr(month_reported_or_occurred)),
  c(expr(month_year_reported_or_occurred),expr(type_of_incident))
  )
```

```         
list_of_tables_to_create_nrls <- list(
  c(expr(PD09)), 
  c(expr(year_reported_or_occurred),expr(month_reported_or_occurred)),
  c(expr(month_year_reported_or_occurred), expr(PD09))
  )
```

```{r}

list_of_tables_to_create_lfpse <- list(c(expr(max_physical_harm_level)))
list_of_tables_to_create_steis <- list(c(expr(year_reported_or_occurred)))
list_of_tables_to_create_nrls <- list(c(expr(PD09)))
```

```{r}

# should LFPSE summary tables be incident level or patient level? (incident/patient)
#note- if LFPSE is not searched, this will not have any effect
summary_tables_incident_or_patient_level <- "patient"
```

## Sampling Strategy

```{r}

# sampling strategy (default/FOI/none)
# TODO: custom
sampling_strategy <- "default"
```

## Run Pipeline

```{r}

source("expand_categorical_filters.R")
```

```{r}

#start flow
source("flow.R")
```
